Homework 5 - Stat 495

### 2022-10-17 homework/hmk4/hmk4Stat495F22.Rmd
Work on Hmk5 and push lab for chapter 17

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
library(rpart)
library(partykit)
library(GGally)
library(broom)
library(lmtest) # for likelihood ratio tests
```

@@

@@

kchouse <- kchouse %>%
  mutate(date = lubridate::mdy(date))

# create a histogram
gf_dhistogram(~ price, data = kchouse) %>%
  gf_labs(title = "Histogram of Prices")

@@

@@

```{r}
# create the training and test set for price
set.seed(1)
n <- nrow(kchouse)
train_index <- sample(1:n, 3/4 * n)
test_index <- setdiff(1:n, train_index)

train <- kchouse[train_index, ]
test <- kchouse[test_index, ]

@@

```{r}
# creating a poisson GLM 
poismod <- glm(price ~ ., data = train, family = poisson(link = log))
msummary(poismod)
```

```{r}
# likelihood ratio test
lrtest(poismod)
```

Using the Likelihood Ratio Test, it appears that the overall model is significant.

```{r, warning=FALSE}
# get MSE of training set
augprice1 <- augment(poismod, type.predict = "response")
mean((augprice1$.fitted - augprice1$price)^2)

#get MSE of test set
test4 <- mutate(test, fitted = predict(poismod, newdata = test, type = "response"))
test4 <-filter(test4, fitted != "NA")
mean((test4$fitted - test4$price)^2)

```
The MSE for the training set is 53,394,691,617 and the MSE for the test set is 49,118,687,275.

Next, we are going to use a Gamma Regression to predict `price`.

```{r}
# fit the gamma regression
gammamod <- glm(price ~ ., data = train, family = Gamma(link = log))
msummary(gammamod)
```
```{r}
# likelihood ratio test
lrtest(gammamod)
```

It appears the the overall model is significant as well.

```{r, warning=FALSE}
# get MSE of training set
augprice2 <- augment(gammamod, type.predict = "response")
mean((augprice2$.fitted - augprice2$price)^2)

#get MSE of test set
test5 <- mutate(test, fitted = predict(gammamod, newdata = test, type = "response"))
test5 <-filter(test5, fitted != "NA")
mean((test5$fitted - test5$price)^2)

@@

The MSE for the training set is 55,085,101,906 and the MSE for the test set is 49,965,056,470 which are both higher than the respective values for the Poisson Regression so that model is better at predicting `price`.

@@

```{r}
# create the regression tree
price.rpart1 <- rpart(price ~ ., data = train, method = "anova")
printcp(price.rpart1)

# print tree to pdf
pdf("price1.pdf", width = 14, height = 14)
plot(as.party(price.rpart1))
dev.off()

```
```{r}
# plot the cp of the regression tree
plotcp(price.rpart1)

# prune the tree
price.prune <- prune(price.rpart1, cp = 0.02)
printcp(price.prune)
```
After plotting the complexity parameter of the regression tree, we attempted to prune the tree.

```{r}
# find the MSE of the training set for default tree
train1 <- mutate(train, fittedtreetrain = predict(price.rpart1))
mean((train1$fittedtreetrain - train1$price)^2)

#find the MSE of the test set for default tree
test1 <- mutate(test, fittedtreetest = predict(price.rpart1, newdata = test))
mean((test1$fittedtreetest - test1$price)^2)
```

From the Regression Tree with default stopping criteria, we calculated the training set MSE to be 66,750,249,627 and the test set MSE to be 67,376,761,596 which are worse than the MSE's we calculated for the Generalized Linear Models.

```{r}
# find the MSE of the training set for the pruned tree
train1 <- mutate(train, fittedtreetrain = predict(price.prune))
mean((train1$fittedtreetrain - train1$price)^2)

# find the MSE of the test set for the pruned tree
test1 <- mutate(test, fittedtreetest = predict(price.prune, newdata = test))
mean((test1$fittedtreetest - test1$price)^2)
```
The MSE for the training set and test set from the pruned tree were 77,345,573,675 and 78,691,909,765, respectively. It appears that the pruned tree is worse at predicting price than the default tree we created so we'll stick with the default one.

Next, we tried taking the log of `price` and creating a new regression tree.

```{r}
# create the tree using log of price
price.rpart2 <- rpart(log(price) ~ ., data = train, method = "anova")
printcp(price.rpart2)

pdf("price2.pdf", width = 14, height = 14)
plot(as.party(price.rpart2))
dev.off()
```

```{r}
# calculate the MSE of the traning set using log price
train2 <- mutate(train, fittedtreetrain2 = predict(price.rpart2),
  traintree2pred = exp(fittedtreetrain2))

mean((train2$traintree2pred - train2$price)^2)
```
However, it appears that the MSE found from predicting the training set is much worse (83,573,000,000), so we will stick with the untransformed `price`.

Next, we will use some stopping critera.

```{r}
# create a regression tree using stopping criteria
price.control <- rpart.control(minbucket = 200, xval = 20, cp = 0.02)
price.rpart3 <- rpart(price ~ ., data = train, method = "anova", control = price.control)
printcp(price.rpart3)

pdf("price3.pdf", width = 14, height = 14)
plot(as.party(price.rpart3))
dev.off()
```

```{r}
# get the MSE of the training set
train3 <- mutate(train, fittedtreetrain = predict(price.rpart3))
mean((train3$fittedtreetrain - train3$price)^2)

# get the MSE of the test set
test3 <- mutate(test, fittedtreetest = predict(price.rpart3, newdata = test))
mean((test3$fittedtreetest - test3$price)^2)
```
The MSE of training set was 101,123,300,000 and the MSE of the test set was 96,700,246,800 which are both worse than the corresponding MSE values of the default regression tree so we would use that tree rather than this one.

>>>>

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
library(rpart)
library(partykit)
library(GGally)
library(broom)
library(ggplot2)
library(lmtest) # for likelihood ratio tests

library(ISLR)
library(glmnet)

library(lars)    # you may need to install some of these (one time only)
library(leaps)   # to use variable selection methods if desired

@@

For this analysis, we used the King County, Washington (State) house sales data set (`kchouse`). Reference for data: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1. There is no information on the source of the data. 
The data set contains the following variables:
\begin{itemize}
\item id - notation for a specific house - Numeric
\item date - date the house was sold - String
\item price - price the house sold for in dollars - Numeric
\item bedrooms - number of bedrooms in house - Numeric
\item bathrooms- number of bathrooms per bedroom - Numeric
\item sqft\textunderscore living - square footage of the home - Numeric
\item sqft\textunderscore lot - square footage of the lot - Numeric
\item floors - total floors (levels) in house - Numeric
\item waterfront - house has a waterfront view - Y/N
\item view - house has been viewed - Numeric
\item condition - How good the condition is (overall) - Numeric
\item grade - overall grade given to housing unit (based on King County grading system: 1 poor, 13 excellent) - Numeric
\item sqft\textunderscore above - square footage of house apart from basement - Numeric
\item yr\textunderscore built - the year the house was built - Numeric
\item yr\textunderscore renovated - the year when the house was generated
\item zipcode - the zipcode the house is in - Numeric
\item lat - Latitude coordinate of house - Numeric
\item long - Longitude coordinate of house - Numeric
\item sqft\textunderscore living15 - living room area in 2015 (may or may not have been affected the lot size area) - Numeric
\item sqft\textunderscore lot15 - lot size area in 2015 - Numeric
\end{itemize}

```{r}
sum(is.na(kchouse$yr_renovated))
```

Before we fit any models, we need to make some adjustments to how the data is being treated by R.

@@

# create a histogram
gf_dhistogram(~ bedrooms, data = kchouse) %>%
  gf_labs(title = "Histogram of Prices")

kchouse <- kchouse %>%
  mutate(date = lubridate::mdy(date),
         waterfront = as.factor(waterfront),
  #       view = as.factor(view),
  #       condition = as.factor(condition),
  #       grade = as.factor(grade),
         zipcode = as.numeric(as.factor(zipcode)))
kchouse <- kchouse %>%
  mutate_at(c('yr_renovated', 'sqft_basement'), ~na_if(.,0))

sum(is.na(kchouse$yr_renovated))/nrow(kchouse)

```{r}
# create a histogram
gf_dhistogram(~ price, data = kchouse) %>%
  gf_labs(title = "Histogram of Prices")

@@

ggplot(data = kchouse, aes(x = lat, y = long)) +
  geom_point()

ggplot(data = kchouse, aes(x = lat, y = long)) +
  geom_point()

kchouse1 <- mutate(kchouse, price = ifelse(price > 500000, 1, 0))

kchouse1 <- kchouse1 %>%
  filter(id != 2402100895) %>%
  select(-c(id,zipcode, yr_renovated,date, sqft_basement))

@@

```{r}
# create the training and test set for price
set.seed(1)
n <- nrow(kchouse1)
train_index <- sample(1:n, 3/4 * n)
test_index <- setdiff(1:n, train_index)

train <- kchouse1[train_index, ]
test <- kchouse1[test_index, ]

@@

```{r}

logmod <- glm(price ~ ., data = train, family = "binomial")
msummary(logmod)
lrtest(logmod)
```

```{r}
augprice1 <- augment(logmod, type.predict = "response")
favstats(~ .fitted, data = augprice1)

@@

```{r}
augprice1 <- mutate(augprice1, binprediction = round(.fitted, 0))
tally(~ binprediction, data = augprice1)
9787/(9787+6410)
```

```{r}
tally(~ price, data = augprice1)
9415/(9415+6782)
with(augprice1, quantile(.fitted, 0.58128))
```

```{r}
augprice1 <- mutate(augprice1, binprediction2 = as.numeric(.fitted > 0.454465))
tally(~ binprediction2, data = augprice1)
```

```{r}
with(augprice1, table(price, binprediction2))
```

```{r}
(8131+5498)/(8131+5498+1284+1284)
```

```{r, warning=FALSE}
# get MSE of training set
augprice1 <- augment(logmod, type.predict = "response")
mean((augprice1$.fitted - augprice1$price)^2)

#get MSE of test set
test4 <- mutate(test, fitted = predict(logmod, newdata = test, type = "response"))
test4 <-filter(test4, fitted != "NA")
mean((test4$fitted - test4$price)^2)

*******************************
```{r}
xPrice <- model.matrix(price ~ ., kchouse1)[, -1]
yPrice <- kchouse1$price

x_train <- model.matrix(price ~ ., train)[, -1]
x_test <- model.matrix(price ~ ., test)[, -1]

y_train <- train %>%
  select(price) %>%
  unlist() %>%
  as.numeric()

y_test <- test %>%
  select(price) %>%
  unlist() %>%
  as.numeric()

grid <- 10^seq(10, -2, length = 100)

ridge_mod <- glmnet(x_train, y_train, family = "binomial", alpha = 0, lambda = grid)

plot(ridge_mod, label = TRUE)
#ridge_pred <- predict(ridge_mod, s = 4, newx = x_test)
#mean((ridge_pred - y_test)^2)

set.seed(1)

cv.out <- cv.glmnet(x_train, y_train, alpha = 0)
bestlam <- cv.out$lambda.min
bestlam

plot(cv.out)

predict(cv.out, type = "coefficients", s = bestlam)

ridge_pred <- predict(ridge_mod, s = bestlam, newx = x_test)
mean((ridge_pred - y_test)^2)

#augprice2 <- augment(ridge_mod, type.predict = "response")
#favstats(~ .fitted, data = augprice2)

@@

```{r}
price.rpart1 <- rpart(price ~ ., data = train, method = "class")
printcp(price.rpart1)

# find the MSE of the training set for default tree
train1 <- mutate(train, predprice = predict(price.rpart1, type = "class"))
tally(predprice ~ price, data = train1)
tally(~ price, data = train1)

#find the MSE of the test set for default tree
test1 <- mutate(test, predprice = predict(price.rpart1, type = "class", newdata = test))
tally(predprice ~ price, data = test1)
tally(~ price, data = test1)
```
```{r}
(8283+5728)/(8283+5728+1132+1054)

(2754+1881)/(2754+1881+377+387)
(3131)/(3131+2268)
```

```{r}
# perhaps make a less complicated one
# see how much you lose
plotcp(price.rpart1)

price.control <- rpart.control(minsplit = 10, cp = 0.017)
price.rpart2 <- rpart(price ~ ., data = train, method = "class", control = price.control)
printcp(price.rpart2)

# find the MSE of the training set for default tree
train1 <- mutate(train, predprice = predict(price.rpart2, type = "class"))
tally(predprice ~ price, data = train1)
tally(~ price, data = train1)

#find the MSE of the test set for default tree
test1 <- mutate(test, predprice = predict(price.rpart2, type = "class", newdata = test))
tally(predprice ~ price, data = test1)
tally(~ price, data = test1)
```

```{r}

### 2022-10-17 homework/hmk5/hmk5Stat495F22.Rmd
Work on Hmk5 and push lab for chapter 17

---
title: "Homework 4 - Stat 495"
author: "Justin Papagelis"
date: "Due Wednesday, Oct. 5th by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
library(rpart)
library(partykit)
library(GGally)
library(broom)
library(ggplot2)
library(lmtest) # for likelihood ratio tests

library(ISLR)
library(glmnet)

library(lars)    # you may need to install some of these (one time only)
library(leaps)   # to use variable selection methods if desired

```

@@

# Homework 4 and 5 Purpose

Homework 4 allows you to practice the two new methods from class recently - GLMs and regression/classification trees. Homework 5 serves as a way to practice our write-up of analyses.

In short, you will be performing some analysis in Homework 4 and then writing it up formally for Homework 5. You will receive some general feedback on Homework 4 as a class, and can use it to refine your models for the write-up in Homework 5. In other words, you may change your models between the two assignments, particularly if you find an issue as you review your work from Homework 4. However, you must submit Homework 4 with potential models for the write-up for both a GLM and tree as discussed below.

# Homework 4 - Analysis

For our analysis, we will use the King County, Washington (State) house sales data set, which I am re-hosting from Kaggle. The Kaggle reference is: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1

@@

A data dictionary taken from Kaggle is provided for your use (separate file).

@@

## Instructions for your Homework 4 submission

The outline for Homework 4 is next, but I want to include information here for you about what you'll need in Homework 5 so that you can include extra information for yourself in your Homework 4 submission, as desired. Look at the end of the assignment for this, and be sure to read it!

Homework 4 requires the following pieces:

* Exploratory Analysis
* GLM - at least 2 models fit with output and assessment
* Tree - at least 2 models fit with output and assessment

It doesn't matter which you tackle first, the GLMs or the trees.

Be sure you understand how to read output for both GLMs and trees, as this is material covered on the midterm.

@@

# Exploratory Analysis

For this analysis, we used the King County, Washington (State) house sales data set (`kchouse`). Reference for data: https://www.kaggle.com/swathiachath/kc-housesales-data/version/1. There is no information on the source of the data. 
The data set contains the following variables:
\begin{itemize}
\item id - notation for a specific house - Numeric
\item date - date the house was sold - String
\item price - price the house sold for in dollars - Numeric
\item bedrooms - number of bedrooms in house - Numeric
\item bathrooms- number of bathrooms per bedroom - Numeric
\item sqft\textunderscore living - square footage of the home - Numeric
\item sqft\textunderscore lot - square footage of the lot - Numeric
\item floors - total floors (levels) in house - Numeric
\item waterfront - house has a waterfront view - Y/N
\item view - house has been viewed - Numeric
\item condition - How good the condition is (overall) - Numeric
\item grade - overall grade given to housing unit (based on King County grading system: 1 poor, 13 excellent) - Numeric
\item sqft\textunderscore above - square footage of house apart from basement - Numeric
\item yr\textunderscore built - the year the house was built - Numeric
\item yr\textunderscore renovated - the year when the house was generated
\item zipcode - the zipcode the house is in - Numeric
\item lat - Latitude coordinate of house - Numeric
\item long - Longitude coordinate of house - Numeric
\item sqft\textunderscore living15 - living room area in 2015 (may or may not have been affected the lot size area) - Numeric
\item sqft\textunderscore lot15 - lot size area in 2015 - Numeric
\end{itemize}

```{r}
sum(is.na(kchouse$yr_renovated))
```

Before we fit any models, we need to make some adjustments to how the data is being treated by R.

```{r}
# explore the data 
# you need to do this before fitting anything!

# submission should demonstrate you explored the data somewhat before 
# fitting the models below

# If there is anything else you should do before fitting models,
# do it here

# change date to a 
# date format

# create a histogram
gf_dhistogram(~ bedrooms, data = kchouse) %>%
  gf_labs(title = "Histogram of Prices")

kchouse <- kchouse %>%
  mutate(date = lubridate::mdy(date),
         waterfront = as.factor(waterfront),
  #       view = as.factor(view),
  #       condition = as.factor(condition),
  #       grade = as.factor(grade),
         zipcode = as.numeric(as.factor(zipcode)))
kchouse <- kchouse %>%
  mutate_at(c('yr_renovated', 'sqft_basement'), ~na_if(.,0))

sum(is.na(kchouse$yr_renovated))/nrow(kchouse)

```

```{r}
# create a histogram
gf_dhistogram(~ price, data = kchouse) %>%
  gf_labs(title = "Histogram of Prices")

gf_boxplot(~ price, data = kchouse)%>%
  gf_labs(title = "Boxplot of Prices")

favstats(~ price, data = kchouse)

ggplot(data = kchouse, aes(x = lat, y = long)) +
  geom_point()

ggplot(data = kchouse, aes(x = lat, y = long)) +
  geom_point()

kchouse1 <- mutate(kchouse, price = ifelse(price > 500000, 1, 0))

kchouse1 <- kchouse1 %>%
  filter(id != 2402100895) %>%
  select(-c(id,zipcode, yr_renovated,date, sqft_basement))

```

```{r}
645000-322000
```

The distribution of `price` is right-skewed with a median of \$450,000 and an IQR is \$323,000. There appears to be many outliers on the high end for `price`. The minimum of `price` is \$78,000 and the maximum is \$7,700,000. Since the distribution is right-skewed, a log-transformation could be useful.

```{r}
# create the training and test set for price
set.seed(1)
n <- nrow(kchouse1)
train_index <- sample(1:n, 3/4 * n)
test_index <- setdiff(1:n, train_index)

train <- kchouse1[train_index, ]
test <- kchouse1[test_index, ]

```

@@

# GLM Model Fitting

```{r}
# choose and fit at least 2 different models for your GLM
# include appropriate output and assessment of their performance

# think ahead: what does a reader need to know to follow your model fitting process?
# you may want to jot down notes for yourself that you'll need later!
```

We are going to first use Poisson Regression to predict `price`.

```{r}

logmod <- glm(price ~ ., data = train, family = "binomial")
msummary(logmod)
lrtest(logmod)
```

```{r}
augprice1 <- augment(logmod, type.predict = "response")
favstats(~ .fitted, data = augprice1)

```

```{r}
augprice1 <- mutate(augprice1, binprediction = round(.fitted, 0))
tally(~ binprediction, data = augprice1)
9787/(9787+6410)
```

```{r}
tally(~ price, data = augprice1)
9415/(9415+6782)
with(augprice1, quantile(.fitted, 0.58128))
```

```{r}
augprice1 <- mutate(augprice1, binprediction2 = as.numeric(.fitted > 0.454465))
tally(~ binprediction2, data = augprice1)
```

```{r}
with(augprice1, table(price, binprediction2))
```

```{r}
(8131+5498)/(8131+5498+1284+1284)
```

```{r, warning=FALSE}
# get MSE of training set
augprice1 <- augment(logmod, type.predict = "response")
mean((augprice1$.fitted - augprice1$price)^2)

#get MSE of test set
test4 <- mutate(test, fitted = predict(logmod, newdata = test, type = "response"))
test4 <-filter(test4, fitted != "NA")
mean((test4$fitted - test4$price)^2)

```

*******************************
```{r}
xPrice <- model.matrix(price ~ ., kchouse1)[, -1]
yPrice <- kchouse1$price

x_train <- model.matrix(price ~ ., train)[, -1]
x_test <- model.matrix(price ~ ., test)[, -1]

y_train <- train %>%
  select(price) %>%
  unlist() %>%
  as.numeric()

y_test <- test %>%
  select(price) %>%
  unlist() %>%
  as.numeric()

grid <- 10^seq(10, -2, length = 100)

ridge_mod <- glmnet(x_train, y_train, family = "binomial", alpha = 0, lambda = grid)

plot(ridge_mod, label = TRUE)
#ridge_pred <- predict(ridge_mod, s = 4, newx = x_test)
#mean((ridge_pred - y_test)^2)

set.seed(1)

cv.out <- cv.glmnet(x_train, y_train, alpha = 0)
bestlam <- cv.out$lambda.min
bestlam

plot(cv.out)

predict(cv.out, type = "coefficients", s = bestlam)

ridge_pred <- predict(ridge_mod, s = bestlam, newx = x_test)
mean((ridge_pred - y_test)^2)

#augprice2 <- augment(ridge_mod, type.predict = "response")
#favstats(~ .fitted, data = augprice2)

```

@@

# Tree Fitting

```{r}
# choose and fit at least 2 different models for your tree
# include appropriate output and assessment of their performance

# think ahead: what does a reader need to know to follow your model fitting process?
# you may want to jot down notes for yourself that you'll need later!
```

```{r}
price.rpart1 <- rpart(price ~ ., data = train, method = "class")
printcp(price.rpart1)

# find the MSE of the training set for default tree
train1 <- mutate(train, predprice = predict(price.rpart1, type = "class"))
tally(predprice ~ price, data = train1)
tally(~ price, data = train1)

#find the MSE of the test set for default tree
test1 <- mutate(test, predprice = predict(price.rpart1, type = "class", newdata = test))
tally(predprice ~ price, data = test1)
tally(~ price, data = test1)
```
```{r}
(8283+5728)/(8283+5728+1132+1054)

(2754+1881)/(2754+1881+377+387)
(3131)/(3131+2268)
```

```{r}
# perhaps make a less complicated one
# see how much you lose
plotcp(price.rpart1)

price.control <- rpart.control(minsplit = 10, cp = 0.017)
price.rpart2 <- rpart(price ~ ., data = train, method = "class", control = price.control)
printcp(price.rpart2)

# find the MSE of the training set for default tree
train1 <- mutate(train, predprice = predict(price.rpart2, type = "class"))
tally(predprice ~ price, data = train1)
tally(~ price, data = train1)

#find the MSE of the test set for default tree
test1 <- mutate(test, predprice = predict(price.rpart2, type = "class", newdata = test))
tally(predprice ~ price, data = test1)
tally(~ price, data = test1)
```

```{r}

```

@@

# Thinking about Homework 5

The eventual Homework 5 submission will include the following sections (along with all code necessary to reproduce your results):

Descriptions of the purpose for each section follow. The idea here is to explain why you'd write each section, and you can work out what needs to be in each in order to fulfill that purpose.

* Exploratory Data Analysis - You are the analyst here. That means you can use variable re-expressions, subsets of observations, and employ other analytic practices (e.g. training/testing data sets) at your discretion to aid in your analysis, so long as you explain your rationale for them. The reader needs to know what you found and what you decided to do about it, because this has impacts on the rest of your analysis. Remember our lessons from the first classes - be sure you look at the data! Here's your chance to share what you found based on how it impacts your analysis.

* GLM and Tree sections - These are new techniques. By having each in their own section, you can focus on your explanation for them one at a time. The reader doesn't know when to use these methods or what they do. You have options that you need to pick for the different techniques (various tuning parameters) - for example, are you using a classification or a regression tree? What tree stopping options are being used? What input variables are you using and why? What type of GLM are you using? How will you be measuring performance? Be sure you discuss what options you are selecting and what made you choose those values. Helping explain this shows your understanding of the techniques (remember the class example that minbucket of 30 was nonsensical for the iris data).

You also want these sections to show off your ability to build models. It is not appropriate to just fit kitchen sink models (as your only model) or accept all default settings without exploring to see if that is really what is best for the task at hand. Your write-up should make it clear what you explored, but you don't have to show every model you considered.

* Model Comparison - There are several ways to compare the models - performance, interpretability, variables involved, etc. Remember you are trying to address the real estate developer's questions of interest, so you probably need to focus on just one model, or maybe you found a way to combine results from a "best" GLM and a "best" tree. The idea for this section is that you need to convey the process used to pick a final model(s) to use to answer those questions, with justification for your choices.

* Conclusion - This section should be a stand alone summary of your analysis. It is where you get to state your final model and a quick summary of the process used to get there. You also need to address the developer's questions, and this is your last place to do that! Remember to flush out the details here. If your final sentence is "Model 5 is the model I choose and it answers your questions", does it? Are you doing your job as the analyst to leave things at that? For that matter, what is Model 5?

* Printing Trees - It is fine to print your trees out to separate .pdfs (just be sure to include them in your submission!). Remember if you want to include the .pdf as an image, you have example code for that. Please do show your code though (so no echo = FALSE), and remember that your work should be reproducible.

>>>>

---
title: "Homework 5 - Stat 495"
author: "YourNameGoesHere"
date: "Due Wednesday, October 19th by midnight"
output:
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, include = FALSE}
library(mosaic)
options(digits = 6)
```

@@

# Homework 5 - Prompt - Write-up for Homework 4

@@

@@

## Write-up Purpose and some Guidance

We want to practice reporting our analyses. You have been contracted to do an analysis, and you prepared some potential models in Homework 4, and now need to report your process and subsequent findings to the client.

Things to think about:

* Your report should be well-organized and proofread.
* Your code should be readable and not run off pages. Employ good commenting practices.
* The entire process must be reproducible.
* Review the class feedback on Homework 4 and adjust your models/thinking as necessary before diving in to the write-up. 
* Think carefully about the organization of the report. Is it useful to have pages of output and THEN a description of what to look for in that output?
* Should you assume the reader knows where values in the R output are?
* If you compute a number, and then write a sentence that says, the MSE is small, will the reader associate that number with being the MSE? What would a better sentence look like? 
* Thinking back to the Tibshirani Writing activity may help you think about ways to improve as well. (Does each of your sections have a purpose? Do you have appropriate signposts, etc.)

## Instructions for your submission

Your submission should include the following sections (along with all code necessary to reproduce your results):

Descriptions of the purpose for each section follow. Do not use this as a set of check boxes for the assignment. Instead, the idea here is to explain why you'd write each section, and you can work out what needs to be in each in order to fulfill that purpose.

* Exploratory Data Analysis - You are the analyst here. That means you can use variable transformations, subsets of observations, and employ other analytic practices (e.g. training/testing data sets) at your discretion to aid in your analysis, so long as you explain your rationale for them. The reader needs to know what you found and what you decided to do about it, because this has impacts on the rest of your analysis. Remember our lessons from the first classes - be sure you look at the data! Here's your chance to share what you found based on how it impacts your analysis.

* GLM and Tree sections - These are new techniques. By having each in their own section, you can focus on your explanation for them one at a time. The developer does not know what these are - you need to explain them at least enough they can follow your discussion. You have options that you need to pick for the different techniques (various tuning parameters) - for example, are you using a classification or a regression tree? What tree stopping options are being used? What input variables are you using and why? What type of GLM are you using? How will you be measuring performance? Be sure you discuss what options you are selecting and what made you choose those values. Helping explain this shows your understanding of the techniques (remember the class example that minbucket of 30 was nonsensical for the iris data).

You also want these sections to show off your ability to build models. It is not appropriate to only fit kitchen sink models or accept all default settings without exploring to see if that is really what is best for the task at hand. Your write-up should make it clear what you explored, but you don't have to show every model you considered. You can do a lot in sentences discussing your process.

* Model Comparison - There are several ways to compare the models - performance, interpretability, variables involved, etc. Remember you are trying to address the real estate developer's questions of interest. You may do that with a focus on just one model, or maybe you found a way to combine results from a "best" GLM and a "best" tree. The idea for this section is that you need to convey the process used to pick a final model(s) to use to answer those questions, with justification for your choices.

* Conclusion - This section should be a stand alone summary of your analysis. It is where you get to state your final model and a quick summary of the process used to get there. You also need to address the developer's questions (if not done before), and this is your last place to do that! Remember to flush out the details here. If your final sentence is "Model 5 is the model I choose and it answers your questions", does it? Are you doing your job as the analyst to leave things at that? For that matter, what is Model 5?

* Printing Trees - It is fine to print your trees out to separate .pdfs (just be sure to include them in your submission!). Remember if you want to include the .pdf as an image, you have example code for that. Please do show your code though (so no echo = FALSE), and remember that your work should be reproducible. The chapter 8 lab solution shows alternatives to *partykit* to make the trees look nice. You can try out *rpart.plot* yourself to see.

* Length - Your submission should be as long as it needs to be, but not unnecessarily long. Plots, etc. are encouraged to help illustrate points, but don't include output that isn't needed. For example, a histogram or densityplot and favstats for each variable is something good to explore, but you shouldn't put that in your submission for every variable. You might need plots to point out outliers you are removing, or maybe you show one plot and then say others were similar. I encourage you to do any additional work in a separate .Rmd from your submission (like, back in your Homework 4 .Rmd).

You may remove these instructions if desired for your submission, but must leave the page on Academic Integrity.

@@

# Introduction

@@

# Exploratory Data Analysis

```{r, include = FALSE}
# Can be included with the introduction
```

@@

# GLM and Results

@@

# Tree and Results

```{r, include = FALSE}
# Can be before or after your GLM
```

# Model Comparison

```{r, include = FALSE}
# Can be woven in above
```

# Conclusion
